Spatial Reasoning and Data Displays

### 2015-01-09 Paper/Draft1/TestingVisualAptitude.Rnw
lineup math

\comment{you can dare to go into a bit of math here - introduce a bit of the lineup math here.  random variable and approximate distribution, explanation for choosing lineups of size 20. }

>>>>

\newtext{In a lineup test, the plot of the data is placed randomly among a set of, generally 19, distractor plots (or {\it null plots}) that are rendered from data generated by a model, without a signal (a null model). This sheet of charts is then shown to human observers, who are asked to identify the display that is ``the most different". If observers identify the plot drawn from the actual data, this can be reasonably taken as evidence that the data it shows is different from the data of other plots.
Let $X$ be the number of observers (out of $n$) who identify the data plot from the lineup. Under the null hypothesis that the data plot is not different from the other plots, $X$ has approximately a Binomial distribution \cite{wickham2010graphical, majumder2013validation}. If $k$ of the observers identify the data plot from the lineup, the probability $P(X \ge k)$ is the $p$-value of the corresponding visual test.

This aspect of lineups provides an important tool in the evaluation of graphical findings. However, the testing situation can be reversed, and lineups allow for an objective evaluation of an individual's visual ability based on the general's population performance on a lineup.

}

\comment{Include how an individual's performance is evaluated. }
